---
title: My stat project
subtitle: a study of awesomeness
author: Bob Hette
date: last-modified
affiliation: Department of Biology
course: Bio8940
course-lec: Julien Martin

# Bibliography style information
bibliography: [proposal_refs.bib, packages.bib]
csl: american-statistical-association.csl

format:
# uncomment if you want this format
#  docx: default   # warning title page not formatted correctly
  bio-uo-stat-pdf: default
  bio-uo-stat-html: default
---

# Introduction

This template is developed for Quarto [@quarto]. You can add tables, figures 
and code using R [@base], Python, Julia or Observables.
For more info, go to "*R way to hell*" [chapter on reproducible reports](https://biostats-uottawa.github.io/R/en/06-quarto.html) and the the Quarto website <https://quarto.org/> 

The intro can be brief (~1/2 page) and should include
- some background of the general ‘big picture’ and specific problem,
- mention of the study system
- specific hypotheses and predictions to be tested. This is key since it will be driving your analysis

# Methods

- Brief outline of data collection
- Clear explanation of statistical methods used to address the hypotheses/predictions outlined in the introduction

In addition to describing analysis in details it is a good practice to cite all R packages used (see the `grateful`package for help with that)


# Results

```{r}
#| label: data-load
dat <- data.frame(a=1:10)
```

No need to show all the code and output here you can use the option "echo: false"
and create table and nice figures

Text and visualizations clearly summarizing your results, using parallel structure to methods. Should include :

- clear graphics representing the data and the model outputs,
- tables reporting statistics
- text describing results
- evaluation of model assumption and model fit

```{r}
#| label: fig-data
#| fig-cap: Amazing plot

plot(dat$a)
```

# Discussion

Need to discuss:

* results
* limitations of approach
* problems with data if any


<!-- 
do not modify below this line,
It will generate the bibliography on a separate page
-->

{{< pagebreak >}}

# References

::: {refs}
:::